Extended Data

### 2022-04-27 doc/manuscript/Dow_manuscript_Nature.Rmd
add ethics declaration, organization of end matter
Added / organized end matter following template of Cook-Patton et al. 2020 Nature

#137

# References {-#References}

# Methods {-#Methods} 
<!--Nature guidelines: Full methods, typically not exceeding 3000 words. May be subdivided by bold headings.-->

## Dendrometer band analysis {-#Dendrometer} 
<!--Study sites -->

@@

## Tree-ring analysis {-#Tree} 
We analyzed tree-ring records for `r n_cores_sites` sites, including our focal sites.
All cores had been previously collected, cross-dated, and measured using standard collection and processing methodologies[@stokes_introduction_1968;@speer_fundamentals_2010].

@@

## Methods References {-#Methods}

# Acknowledgements {-#Acknowledgements} 
We gratefully acknowledge all researchers who assisted with data collection in the field and laboratory, particularly Tsun Fung Au, Joshua Bregy, James Dickens, Karen Heeter, Anna Hennage, Daniel King, James McGee, Benjamin Lockwood, Jennifer McGarvey, Victoria Meakem, Josh Oliver, Jessica Shue, Karly Schmidt-Simard, Brandon Strange, Alyssa Terrell, Brynn Taylor, Michael Thornton, Senna Robeson, Matt Wenzel, and Luke Wylie. 
Thanks to David A. Orwig, members of the ForestGEO Ecosystems & Climate Lab at SCBI, and four anonymous reviewers for helpful feedback.
The research was funded by ForestGEO (Smithsonian). 
Collection of tree-ring samples was funded by a USDA Agriculture and Food Research Initiative grant 2017-67013-26191 and from the Indiana University Vice Provost for Research Faculty Research Program.

# Author Contributions {-#Author}

@@

>>>>

# References {-}

# Methods {-} 
<!--Nature guidelines: Full methods, typically not exceeding 3000 words. May be subdivided by bold headings.-->

## Dendrometer band analysis {-} 
<!--Study sites -->

@@

## Tree-ring analysis {-} 
We analyzed tree-ring records for `r n_cores_sites` sites, including our focal sites.
All cores had been previously collected, cross-dated, and measured using standard collection and processing methodologies[@stokes_introduction_1968;@speer_fundamentals_2010].

@@

## Methods References {-}

# Acknowledgements {-} 
We gratefully acknowledge all researchers who assisted with data collection in the field and laboratory, particularly Tsun Fung Au, Joshua Bregy, James Dickens, Karen Heeter, Anna Hennage, Daniel King, James McGee, Benjamin Lockwood, Jennifer McGarvey, Victoria Meakem, Josh Oliver, Jessica Shue, Karly Schmidt-Simard, Brandon Strange, Alyssa Terrell, Brynn Taylor, Michael Thornton, Senna Robeson, Matt Wenzel, and Luke Wylie. 
Thanks to David A. Orwig, members of the ForestGEO Ecosystems & Climate Lab at SCBI, and four anonymous reviewers for helpful feedback.
The research was funded by ForestGEO (Smithsonian). 
Collection of tree-ring samples was funded by a USDA Agriculture and Food Research Initiative grant 2017-67013-26191 and from the Indiana University Vice Provost for Research Faculty Research Program.

# Author Information{-}

## Contributions {-}

@@

## Corresponding Author {-}

Correspondence to [Kristina J. Anderson-Teixeira](teixeirak@si.edu).

# Ethics declarations {-}
## Competing interests {-}

The authors declare no competing interests.
